Ellicular galaxies and their (non {\"u}ber-massive) black holes

### 2015-09-17 papers/ellicular/ellicular.tex
nemo

\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}

@@

\begin{abstract}
The classification early-type galaxy includes both elliptically-shaped and lenticular galaxies, 
with the latter composed of a spheroid, or bulge, of stars encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value. 
However, several studies only consider spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii -- creating an inner bulge -- 
and they reject decompositions if the disc remains embedded within the spheroid, labeling them as ``unphysical''. 
Here we show that these rejected models correctly reproduce the photometric and kinematic properties of a class of early-type galaxy 
with intermediate-scale disc. 
Intermediate-scale discs have often been confused with large-scale discs, 
and as a consequence the disc luminosities have been considerably overestimated 
and their spheroid luminosities underestimated. 
%intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
%Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
%and their spheroid luminosities underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of intermediate-scale disc galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
When intermediate-scale disc galaxies are properly modeled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram, 
thereby resolving previous anomalies. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

%We refer to the last case as an ellicular galaxy. 

@@

However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modellers, 

@@

The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies.
%and creates the need for a new subclass to help bridge the divide. 

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{images/discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a lenticular galaxy, composed of a bulge encased in a large-scale disc. 
The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. }
\label{fig:model}
\end{center}
\end{figure}

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of early-type galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis (when) available from the literature. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available.} \citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
whereas the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a fain edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
The surface brightness profile (Figure \ref{fig:n3115}) is well described with a S\'ersic-spheroid \citep{sersic1963},  
an intermediate-sized exponential-disc, and a Gaussian-ring.

\subsection{NGC 1332}
The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
with the ellipticity profile indicating the presence of an intermediate-scale disc, 
although in this case no nuclear component was identified from our photometric analysis. 
The authors of this paper were not able to find any extended kinematic profile or map 
for this galaxy in the literature. 
The data within the innermost $6~\rm arcsec$ were excluded from the fit 
because possibly affected by the presence of a partially depleted core.
The spheroidal component of NGC 1332 is modelled with a S\'ersic profile. 
The highly inclined intermediate-scale disc is better described with a $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function \citep{pastrav2013a}. 
Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
with a spheroid-to-total ratio of $0.95$.
\cite{rusli2011} did not identify the extent of the intermediate-scale disc, 
and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
with a spheroid-to-total ratio of $0.43$.
Based on such bulge-disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
by an order of magnitude along the black hole mass direction. 
In Section \ref{sec:mm} we show that, according to our decomposition, 
NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
for early-type galaxies.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
\caption{The galaxy NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = exponential (disc), gray = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

@@

\section{Implications}
\label{sec:impl}
Past models that ``forcedly'' described intermediate-scale disc galaxies using an inner bulge 
encased within a large-scale disc 
commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
and underestimate the size of the spheroid by a factor of $6-10$, 
although more ``extreme'' cases can be found. \\
\cite{lasker2014data} fit the galaxy NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$; 
we described this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtained a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. \\
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$. \\
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + inner disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$.

@@

Recently, a handful of intermediate-scale disc galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 

@@

For early-type galaxies, the spheroid luminosity and the galaxy luminosity 
can be used to predict the black hole mass with the same level of accuracy\footnote{However, 
when considering all galaxies (early- and late-type) irrespective of their morphological type, 

@@

(Savorgnan et al.~\emph{submitted}). 

@@

due to an inaccurate spheroid/disc decomposition. 

@@

\subsection{Origin of compact massive galaxies}
Acknowledging the correct structure of intermediate-scale disc galaxies is also important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
when cold gas inflows produced short and intense bursts of star formation that created the cores of galaxies. 
These naked and compact cores, named ``red nuggets'' \citep{damjanov2009}, have been observed at high-redshift with sizes of $1-2~\rm kpc$ \citep{vandokkum2008}.
In the second phase (last $10~\rm Gyr$), stellar discs and stellar envelopes 
were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of $2-20~\rm kpc$. 
Today's Universe is populated by an abundance of compact, massive spheroids, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies. 
Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc -- 
rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
The other compact massive spheroids of today's Universe belong to some intermediate-scale disc galaxies. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact galaxies 
with intermediate-scale discs and purely old ($>10~\rm Gyr$) stellar populations. 
These galaxies have undergone the lowest degree of disc growth. \\
In addition to the observational clues as to the actual physical components in ellicular galaxies, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope. 
If they were such three-component systems, then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of $0.1-0.2~\rm kpc$, 
according to past decompositions) originated in the first $4~\rm Gyr$ 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact ($1-2~\rm kpc$). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact ellicular galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact ellicular galaxy quickly assembled ``in-situ'' in a very young Universe 
and experienced very little evolution over the last $10~\rm Gyr$.

@@

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/}
%\caption{}
%\label{fig:}
%\end{center}
%\end{figure}

>>>>

%\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
\title[Ellicular galaxies]{Ellicular galaxies and their (non {\"u}ber-massive) black holes}

@@

\begin{abstract}
The classification early-type galaxy includes both elliptically-shaped and lenticular galaxies, 
with the latter composed of a spheroid, or bulge, of stars encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value. 
However, several studies only consider spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii -- creating an inner bulge -- 
and they reject decompositions if the disc remains embedded within the spheroid, labeling them as ``unphysical''. 
Here we show that these rejected models correctly reproduce the photometric and kinematic properties of a class of early-type galaxy 
%with intermediate-scale disc. 
%Intermediate-scale discs have often been confused with large-scale discs, 
%and as a consequence the disc luminosities have been considerably overestimated 
%and their spheroid luminosities underestimated. 
intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
and their spheroid luminosities underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of ellicular galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
When ellicular galaxies are properly modeled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram, 
thereby resolving previous anomalies. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

We refer to the last case as an ellicular galaxy. 

@@

However, the class of ellicular galaxies has been missed by many galaxy modellers, 

@@

The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies 
and creates the need for a new subclass to help bridge the divide. 

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{images/discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a lenticular galaxy, composed of a bulge encased in a large-scale disc. 
The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. 
We refer to the last case as an ellicular galaxy.}
\label{fig:model}
\end{center}
\end{figure}

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis (when) available from the literature. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} are small. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
whereas the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a fain edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with a $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function.

\subsection{NGC 1332}
The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
with the ellipticity profile indicating the presence of an intermediate-scale disc, 
although in this case no nuclear component was identified from our photometric analysis. 
The authors of this paper were not able to find any extended kinematic profile or map 
for this galaxy in the literature. 
The data within the innermost $6~\rm arcsec$ were excluded from the fit 
because possibly affected by the presence of a partially depleted core.
The surface brightness profile of NGC 1332 is well described with a S\'ersic-spheroid plus
a $n<1$ S\'ersic-disc. 
Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
with a spheroid-to-total ratio of $0.95$.
\cite{rusli2011} did not identify the extent of the intermediate-scale disc, 
and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
with a spheroid-to-total ratio of $0.43$.
Based on such bulge-disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
by an order of magnitude along the black hole mass direction. 
However, in Section \ref{sec:mm} we show that, according to our decomposition, 
NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
for early-type galaxies.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
\caption{The galaxy NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = S\'ersic (disc), gray = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

@@

\section{Implications}
\label{sec:impl}
Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
encased within a large-scale disc 
commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
and underestimate the size of the spheroid by a factor of $6-10$, 
although more ``extreme'' cases can be found. \\
\cite{lasker2014data} fit the galaxy NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$; 
we described this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtained a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. \\
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$. \\
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + inner disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$.

@@

Recently, a handful of ellicular galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 

@@

\emph{For early-type galaxies, the spheroid luminosity and the galaxy luminosity 
can be used to predict the black hole mass with the same level of accuracy\footnote{Note that 
\cite{lasker2014anal} reported that the spheroid luminosity and the galaxy luminosity are equally good tracers of the black hole mass 
irrespective of the galaxy morphological type, but their sample of 35 galaxies contained only 4 spiral galaxies. 
However, using a sample of 45 early-type and 17 spiral galaxies, 
Savorgnan et al.~(\emph{submitted}) shows that, when considering all galaxies irrespective of their morphological type, 

@@

(Savorgnan et al.~submitted). 

@@

due to an inaccurate spheroid/disc decomposition. }

@@

\subsection{Origin of compact massive galaxies}
Acknowledging the correct structure of ellicular galaxies is also important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
when cold gas inflows produced short and intense bursts of star formation that created the cores of galaxies. 
These naked and compact cores, named ``red nuggets'' \citep{damjanov2009}, have been observed at high-redshift with sizes of $1-2~\rm kpc$ \citep{vandokkum2008}.
In the second phase (last $10~\rm Gyr$), stellar discs and stellar envelopes 
were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of $2-20~\rm kpc$. 
Today's Universe is populated by an abundance of compact, massive spheroids, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies. 
Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc -- 
rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
The other compact massive spheroids of today's Universe belong to some ellicular galaxies. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
with purely old ($>10~\rm Gyr$) stellar populations. 
These galaxies have undergone the lowest degree of disc growth. \\
In addition to the observational clues as to the actual physical components in ellicular galaxies, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope. 
If they were such three-component systems, then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of $0.1-0.2~\rm kpc$, 
according to past decompositions) originated in the first $4~\rm Gyr$ 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact ($1-2~\rm kpc$). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact ellicular galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact ellicular galaxy quickly assembled ``in-situ'' in a very young Universe 
and experienced very little evolution over the last $10~\rm Gyr$.

@@

\subsection{Ellicular galaxies in the Hubble grid}
The existence of the oft-overlooked, intermediate-scale discs presented here exposes a likely continuum of disc sizes in early-type galaxies 
as opposed to a dichotomy of nuclear discs versus large-scale discs. 
The presence of these intermediate-scale discs also blurs the distinction between elliptical (E) and lenticular (S0) galaxies 
and arguably creates the need for a new subclass which bridges this divide.  
While expanding the galaxy nomenclature beyond ellipticals with possible nuclear discs, and lenticulars with large-scale discs, 
to include something like {\it elliculars} with intermediate-scale discs will be helpful 
for distinguishing among the different early-type galaxies with different disk scale-lengths, 
it should be remembered that just as portions of the electromagnetic spectrum are labelled according to their different wavelengths, 
there is still an underlying continuum.  
Similarly, binning early-type galaxies as either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact that a continuum exists.  
Importantly, in the case of early-type galaxies with intermediate scale discs, 
this particular rotation-classification depends on the galaxy's radial range probed.  
There is thus a need for more than two bins (E vs.~S0, or SR vs.~FR). \\
The existence of intermediate-scale discs is not only important for our understanding of disc growth in general, 
but accounting for such components impacts upon our broader understanding of galaxy structure.  
It has recently been argued \citep{graham2014review} that the classification scheme for elliptical galaxies 
should not be their apparent axis ratio as seen on the plane of the sky, 
but rather early-type galaxies should be quantified by their spheroid-to-total flux ratio, 
with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies.   
While spiral galaxies display a range of spheroid-to-total flux ratios from 0 to $\sim$3/4, 
lenticular galaxies display a range from $\sim$3/4 to $\sim$0.1 (see \citealt{laurikainen2010}).   
The spheroid-to-total flux ratio is an important quantity, and its broad range observed in lenticular galaxies 
has led to a resurgence of \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) Hubble comb, 
in which both late-type galaxies (i.e.~spiral galaxies) and lenticular galaxies form the arms of an expanded Hubble tuning fork, 
with an additional arm for disc galaxies hosting anaemic spiral patterns (see \citealt{cappellari2011kmdr-MNRAS} and \citealt{kormendybender2012}).  
However because every spiral Hubble type (e.g.~Sa, Sb, Sc) has a broad range of spheroid-to-total ratio 
(e.g.~\citealt{grahamworley2008}, and references therein), 
and because this information is not captured by the Hubble comb, 
a grid of spiral type (predominantly determined by the spiral arms) versus spheroid-to-total ratio is also useful for classifying galaxies.   
In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale discs in such a Hubble grid \citep{graham2014review}, 
revealing how they are related to the other galaxies.  
Aside from the pure elliptical galaxies, each galaxy type displays a range of spheroid-to-total flux ratio.  
Rather than a scheme in which the spiral morphological type (a, b, c, etc.) changes if the spheroid-to-total ratio changes (as in the Hubble comb), 
here the galaxy type is linked to the nature and winding of the spiral arms which has been the primary criteria used 
to classify spiral galaxies over the last half century \citep{sandage1961}.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/Hubble-grid-2/Hubblegrid.pdf}
\caption{The Hubble grid \citep{graham2014review}, 
which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type. 
Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
\label{fig:grid}
\end{center}
\end{figure}
